Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Structure

### 2017-03-08 documents/TriangleScenarioArXiv/ts.tex
refined the Fritz refinements

\PassOptionsToPackage{justification=justified}{caption}
% === Revtex Declaration ===
\documentclass[aps, 10pt, english, twoside, pra, nofootinbib, tightenlines, longbibliography]{revtex4-1}

@@

    The manuscript is organized into the following sections: \Cref{sec:causal_compatibility} recalls important notions from causal inference theory and sets up the notation to be used. \Cref{sec:triangle_structure} discusses the Triangle structure and provides an overview of existing research; identifying its stark differences from the Bell structure and motivating why the Triangle structure was chosen as a case study. \Cref{sec:fritz_distribution} defines and discusses a singularly-quantum correlation first concieved of by \citet{Fritz_2012}, which we term the \term{Fritz distribution}. The Fritz distribution was proven to be non-classical without the use of inequalities --- this report fills in the desired missing inequalities. \Cref{sec:inflation_technique} briefly summaries the Inflation Technique in the specific context of this work. Although the summary presented here is designed to be self-standing, a much more pedagogical introduction is offered by the original work~\cite{Inflation}. \Cref{sec:deriving_inequalities} demonstrates how the inflation technique can be used to derive causal compatibility inequalities for the Triangle structure that are violated by quantum-accessible distributions. A sample of these inequalities are presented at the end of \cref{sec:deriving_inequalities} as well as in \cref{sec:web_inequality,sec:symmetic_web_inequality}. Finally, \cref{sec:violations_noise} introduces the method for parameterizing the space of quantum-accessible distributions which we used to numerically optimize against our derived inequalities in search of stronger types of non-classicality. Additionally, the Fritz distribution is subjected to noise in order to measure the robustness of the derived inequalities.

    \section{Causal Compatibility}
    \label{sec:causal_compatibility}
    The task of causal inference aims to determine the set of potentially observable probability distribution compatible with some hypothesis about causal relationships. whether or not a given family of observed probability distributions can be explained by a proposed causal mechanism~\cite{Pearl_2009}. If a set of observed distributions can be explained by the hypothesized causal mechanism, then the observations are said to be \textit{compatible} with the causal mechanism. In order to define compatibility rigorously, we first need to formally define what is meant by ``set of observations''.

@@

@@

    Upon reflection, the Fritz distribution can rightly be considered slightly manufactured. The phenomenology associated with Bell non-locality or Bell incompatibility are well understood; examining these distributions under a Triangle structure embedding offers no additional perspective onto the types of resources made accessible by quantum mechanics. Therefore, it is desirable to find incompatible quantum distributions that are qualitatively different than those previously considered for the Bell structure. \citet{Fritz_2012} presented the following problem: \textit{Find an example of non-classical quantum correlations in the Triangle structure together with a proof of its non-classicality which does not hinge on Bell’s Theorem.}\footnote{In the way Fritz defines, \textit{non-classical} correlations are the class of \textit{incompatible} correlations.} The problem is understandably stated ambiguously as it is not yet entirely clear how to distinguish between non-classical distributions on differing causal structures. In order to remove some of the ambiguity, consider the following refinements of the problem:
    \begin{enumerate}[label=\textbf{R.\arabic*}]
        \item \label{r:1} Find proofs for causal incompatibility of quantum distributions on the Triangle structure that are \textit{not} reliant on perfect correlations.
        \item \label{r:2} Find incompatible quantum distributions on the Triangle structure that satisfy all Bell structure inequalities under Fritz-type embeddings.
        \item \label{r:3} Find incompatible quantum distributions that require entanglement in more than one shared state.
    \end{enumerate}
    The remainder of this document focuses on a positive solution to \ref{r:1} but leaves \ref{r:2} and \ref{r:3} partially unanswered.

    \section{Inflation Technique}
    \label{sec:inflation_technique}
    The \term{Inflation Technique}, invented by \citet{Inflation} and inspired by the \textit{do calculus} and \textit{twin networks} of \citet{Pearl_2009}, is a family of causal inference techniques that can be used to determine if a marginal model $\prob^{\mscenario}$ is compatible or incompatible with a given causal structure $\graph$. As a preliminary summary, the inflation technique begins by \textit{augmenting} a causal structure with additional copies of its nodes, producing an \textit{inflated} causal structure, and then exposes how causal inference tasks on the inflated causal structure can be used to make inferences on the original causal structure. As a example, inflations of the Triangle structure are depicted in \cref{fig:inflations}. Copies of nodes in the inflated causal structure are distinguished by an additional subscript called the \term{copy-index}. For example node $A$ of \cref{fig:triangle_structure} has copies $A_1, A_2, A_3, A_4$ in the \textit{Web inflation} of \cref{fig:the_web_inflation}. All such copies are deemed equivalent via a \term{copy-index equivalence} relation denoted `$\sim$'. A copy-index is effectively arbitrary, so we will refer to an arbitrary inflated copy of $A$ as $A'$.
    \[ A \sim A_1 \sim A' \not\sim B \sim B_1 \sim B' \]
    We preemptively generalize the notion of copy-index equivalence to other mathematical objects like sets, graphs, and groups by saying that $X \sim Y$ if and only if $X = Y$ upon removal of the copy-index. Equipped with the common graph-theoretic terminology and notation of \cref{def:graph_terms}, an inflation can be formally defined as follows:
    \begin{definition}
        An \term{inflation} of a causal structure $\graph$ is another causal structure $\graph'$ such that:
        \[ \forall n' \in \nodes': \AnSub[\graph']{n'} \sim \AnSub[\graph]{n} \eq \label{eq:inflation_defn}\]
        Verbally, for each inflated node $n'$, the ancestral sub-graph of $n'$ in $\graph'$ is equivalent to its counterpart in $\graph$ up to copy-index.
    \end{definition}
    The motivation behind this definition is that if the ancestry of each node $n'$ in $\graph'$ plays the \textit{exact same} role as the ancestry of its source copy $n$ in $\graph$, then every compatible joint distribution $\prob[\nodes]$ on $\graph$ can be used to \textit{create} compatible joint distributions on $\graph'$.

    A pre-injectable set $N'$ is of primal importance to the inflation technique because any distribution over $N'$ will factorize according to graphical $d$-separation conditions~\cite{Pearl_2009},
    \[ \prob[N'] = \prob[\coprod_i N'_i] = \prod_{i}\prob[N'_i] \]
    Application of the inflation lemma to linear inequalities constraining pre-injectable distributions $\prob[N']$ transforms those inequalities into polynomial inequalities over the injectable distributions, allowing one to replace all terms with probability distributions defined over variables in $\nodes$. Throughout the body of this work, we let $\PreInj[\graph]{\graph'}$ denote the set of all pre-injectable sets. Naturally, the pre-injectable sets will define a marginal scenario $\mscenario$ that in \cref{sec:deriving_inequalities} will be used to derive compatibility inequalities\footnote{Analogously for a marginal scenario $\mscenario$, the pre-injectable sets $\PreInj[\graph]{\graph'}$ form an \textit{abstract simplicial complex}. Therefore, in practice, it is completely sufficient to focus on the maximal pre-injectable sets}.

    \section{Deriving Inequalities}
    \label{sec:deriving_inequalities}

@@

    \subsection{The Marginal Problem as a Linear Program}
    \label{sec:marginal_linear}

@@

    \subsubsection{Events \& Outcomes}
    To every discrete random variable $v$ there corresponds a prescribed set of \term{outcomes} $O_v$. We also define the set of all \term{events over $v$} $\Events{v}$\footnote{In the language of sheaf-theory, $\Events{v}$ is the \textit{sheaf of events}~\cite{Abramsky_2011}.} to be the set of all functions $s : \bc{v} \to O_v$ each representing the event that a measurement on $v$ was made where $s\br{v} \in O_v$ was observed.
    \[ \Events{v} \defined \bc{s : \bc{v} \to O_v} \]
    Evidently, $\Events{v}$ and $O_v$ have a one-to-one correspondence and this distinction can be confounding. There is rarely any harm in referring synonymously to either as outcomes. Nonetheless, a sheaf-theoretic treatment of contextuality~\cite{Abramsky_2011} demands the distinction.
    Specifically for this work, the distinction becomes essential for our discussion and exploit of marginal symmetries in \cref{sec:symmetric_inequalities}. As a natural generalization we define the event over a collection of random variables $V = \bc{v_1, \ldots, v_n}$ in a parallel manner,
    \[ \Events{V} \defined \bc{s: V \to O_{V} \mid \forall i : s\br{v_i} \in O_{v_i} } \eq \label{eq:outcome_space}\]
    Each event $s$ can be compactly represented as a set of mappings over each element of $V$.
    \[ s = \bc{v_1 \mapsto s\br{v_1}, \ldots, v_k \mapsto s\br{v_k}} = \bc{v_i\mapsto s\br{v_i}}_{i = 1}^{k} \]
    The domain $\Dom{s}$ of an event $s$ is the set of random variables it valuates, i.e. if $s \in \Events{V}$, then $\Dom{s} = V$. Under this framework, a probability distribution $\prob[V]$ can be considered as a map from $\Events{V}$ to the unit interval $\bs{0,1}$.
    \begin{example}
        Let $s \in \Events{V}$ be an event over $V$, a probability distribution $\prob[V]$ over $V$ will assign a non-negative probability $\prob[V][s]$ to $s$. Let $V = \bc{v_1, v_2}$ with each $v \in V$ having $3$ distinct outcomes $O_v = \bc{0,1,2}$. Furthermore let $f \in \Events{V}$ be the event $\br{v_1 \mapsto 2, v_2 \mapsto 1}$. The following notations are interchangeable,
        \[ \prob[][s] = \prob[\Dom{s}][s] = \prob[V][s] = \prob[v_1, v_2][s] = \prob[][v_1 \mapsto s_1\br{v_1}, v_2 \mapsto s_2\br{v_2}] = \prob[][v_1 = 2, v_2 = 1] = \prob[v_1v_2][21] \]
        Each of which should be read as ``the probability that $v_1$ got outcome $2$ and $v_2$ got outcome $1$''
    \end{example}
    The marginal problem inherently depends on the concept of probabilistic marginalization. This concept can be understood at the level of events; one event $s \in \Events{V}$ can be ``marginalized'' or restricted to a smaller event $s' \in \Events{W}$ whenever $W \subseteq V$.
    \begin{definition}
    \label{def:section_restriction}
    For every $W \subseteq V$ and $s \in \Events{V}$, the \term{restriction of $s$ onto $W$} (denoted $s|_{W} \in \Events{W}$) is the event in $\Events{W}$ that \textit{agrees} with each of $s$'s assignments for variables in $W$.
    \[ \forall v \in W : s|_{W}\br{v} = s\br{v} \]
    \end{definition}
    % \begin{definition}
    % \label{def:section_compatible}
    % The events $s_{V} \in \Events{V}$ and $s_{W} \in \Events{W}$ are said to be \term{compatible} events if they agree on their valuations of $V \cap W$. Compatibility will be denoted with the infix `$\com$'.
    % \[ s_{V} \com s_{W} \iff {s_{V}}|_{V\cap W} = {s_{W}}|_{V\cap W} \]
    % \end{definition}
    % \begin{definition}
    % \label{def:section_extendable}
    % It $s_V \in \Events{V}$ and $s_W \in \Events{W}$ compatible events and $W \subseteq V$ then $s_W$ is said to be \term{extendable} to $s_V$. Extendability will be denoted with the infix `$\ext$'.
    % \[ s_W \ext s_V \iff s_W \com s_V, W \subseteq V \]
    % Extendability is dual to the notion of a \term{restriction} of $s_V$; $s_V$ can be restricted to $s_W$ ($s_V \res s_W$) if and only if $s_W$ is extendable to $s_V$.
    % \end{definition}

@@

    \subsection{Triangle Structure Inequalities}
    \label{sec:found_inequalities}

    \subsection{Symmetric Inequalities}
    \label{sec:symmetric_inequalities}

>>>>

% === Revtex Declaration ===
\documentclass[aps, 10pt, english, twoside, pra, nofootinbib, tightenlines, longbibliography]{revtex4-1}

@@

    The manuscript is organized into the following sections: \Cref{sec:causal_compatibility} recalls important notions from causal inference theory and sets up the notation to be used. \Cref{sec:triangle_structure} discusses the Triangle structure and provides an overview of existing research; identifying its stark differences from the Bell structure and motivating why the Triangle structure was chosen as a case study. \Cref{sec:fritz_distribution} defines and discusses a singularly-quantum correlation first concieved of by \citet{Fritz_2012}, which we term the \term{Fritz distribution}. The Fritz distribution was proven to be non-classical without the use of inequalities --- this report fills in the desired missing inequalities. \Cref{sec:inflation_technique} briefly summaries the Inflation Technique in the specific context of this work. Although the summary presented here is designed to be self-standing, a much more pedagogical introduction is offered by the original work~\cite{Inflation}. \Cref{sec:deriving_inequalities} demonstrates how the inflation technique can be used to derive causal compatibility inequalities for the Triangle structure that are violated by quantum-accessible distributions. A sample of these inequalities are presented at the end of \cref{sec:found_inequalities} (specifically \cref{eq:ww_ineq}) as well as in \cref{sec:web_inequality,sec:symmetic_web_inequality}. Finally, \cref{sec:violations_noise} introduces the method for parameterizing the space of quantum-accessible distributions which we used to numerically optimize against our derived inequalities in search of stronger types of non-classicality. Additionally, the Fritz distribution is subjected to noise in order to measure the robustness of the derived inequalities.

    \section{Causal Compatibility}
    \todo[TC]{Talk to Elie about the varying notions of compatibility}
    \label{sec:causal_compatibility}
    The task of causal inference aims to determine the set of potentially observable probability distribution compatible with some hypothesis about causal relationships. whether or not a given family of observed probability distributions can be explained by a proposed causal mechanism~\cite{Pearl_2009}. If a set of observed distributions can be explained by the hypothesized causal mechanism, then the observations are said to be \textit{compatible} with the causal mechanism. In order to define compatibility rigorously, we first need to formally define what is meant by ``set of observations''.

@@

    \section{Bell Structure}
    \label{sec:bell_structure}
    \todo[TC]{Review of Bell structure, Tsirelson-box, CHSH inequality}

@@

    Upon reflection, the Fritz distribution can rightly be considered slightly manufactured. The phenomenology associated with Bell non-locality or Bell incompatibility are well understood; examining these distributions embedded in the Triangle structure offers no additional perspective onto the types of entanglement resources made accessible by quantum mechanics. Therefore, it is desirable to find incompatible quantum distributions that are qualitatively different than those previously considered for the Bell structure. Pursuant to this, \citet{Fritz_2012} presented the following problem~\cite[Problem 2.17]{Fritz_2012}:%TODO figure out best way to link to this problem

    \term{Fritz's Problem}: Find an example of non-classical quantum correlations in the Triangle structure together with a proof of its non-classicality which does not hinge on Bell’s theorem.\footnote{In the way Fritz defines, \textit{non-classical} correlations are the class of \textit{incompatible} correlations.}

    Understandably, Fritz's Problem is stated ambiguously as it is not yet entirely clear how to distinguish between non-classical distributions on differing causal structures. The remainder of this paper focuses on our advancement toward solving Fritz's Problem. \Cref{sec:conclusions} proposes three refinements of Fritz's Problem which are to be labeled \ref{r:1},\ref{r:2} and \ref{r:3} respectively. Specifically, \ref{r:1} embodies the degree in which the results of \cref{sec:found_inequalities} solve Fritz's problem while \ref{r:2} and \ref{r:3} characterize interpretations of Fritz's Problem that remain partially solved.

    \section{Triangle Structure Inequalities}
    \label{sec:found_inequalities}

    \section{Symmetric Inequalities}
    \label{sec:symmetric_inequalities}

    For the Triangle structure in particular, the variable permutation group is simply the set of permutations on $A, B, C$: $\Phi\br{\mscenario} = \Perm{A, B, C}$. For the Web inflation (\cref{fig:the_web_inflation}), we have obtained $\gp\br{\PreInj[\graph]{\graph'}}$ which is an order $48$ group with the following $4$ generators:
    \begin{equation*}
    \begin{aligned}[c]
    &\hspace{1mm}\varphi_1 \\
    A_1 &\to A_4 \\A_2 &\to A_3 \\A_3 &\to A_2 \\A_4 &\to A_1 \\B_1 &\to B_4 \\B_2 &\to B_3 \\B_3 &\to B_2 \\B_4 &\to B_1 \\C_1 &\to C_4 \\C_2 &\to C_3 \\C_3 &\to C_2 \\C_4 &\to C_1
    \end{aligned}
    \quad
    \begin{aligned}[c]
    &\hspace{1mm}\varphi_2 \\
    A_1 &\to A_1 \\A_2 &\to A_3 \\A_3 &\to A_2 \\A_4 &\to A_4 \\B_1 &\to C_1 \\B_2 &\to C_3 \\B_3 &\to C_2 \\B_4 &\to C_4 \\C_1 &\to B_1 \\C_2 &\to B_3 \\C_3 &\to B_2 \\C_4 &\to B_4
    \end{aligned}
    \quad
    \begin{aligned}[c]
    &\hspace{1mm}\varphi_3 \\
    A_1 &\to C_1 \\A_2 &\to C_2 \\A_3 &\to C_3 \\A_4 &\to C_4 \\B_1 &\to A_1 \\B_2 &\to A_2 \\B_3 &\to A_3 \\B_4 &\to A_4 \\C_1 &\to B_1 \\C_2 &\to B_2 \\C_3 &\to B_3 \\C_4 &\to B_4
    \end{aligned}
    \quad
    \begin{aligned}[c]
    &\hspace{1mm}\varphi_4 \\
    A_1 &\to A_1 \\A_2 &\to A_2 \\A_3 &\to A_3 \\A_4 &\to A_4 \\B_1 &\to B_2 \\B_2 &\to B_1 \\B_3 &\to B_4 \\B_4 &\to B_3 \\C_1 &\to C_3 \\C_2 &\to C_4 \\C_3 &\to C_1 \\C_4 &\to C_2
    \end{aligned}
    \end{equation*}
    % ((3, 2, 1, 0, 7, 6, 5, 4, 11, 10, 9, 8),
    %  (0, 2, 1, 3, 8, 10, 9, 11, 4, 6, 5, 7),
    %  (8, 9, 10, 11, 0, 1, 2, 3, 4, 5, 6, 7),
    %  (0, 1, 2, 3, 5, 4, 7, 6, 10, 11, 8, 9))
    It is easy to verify that $\varphi_1, \varphi_2, \varphi_3, \varphi_4$ are all automorphisms of the web inflation. Moreover they stabilize the pre-injectable sets of \cref{eq:pre_injectable_triangle_structure_web}. Importantly,
    \[ \gp\br{\PreInj[\graph]{\graph'}} \sim \Perm{A,B,C} \]
    To see this, $\varphi_1$ and $\varphi_4$ become the identity element $\ident$ in $\Perm{A,B,C}$ upon removal of the copy-index, leaving $\varphi_2$ to generate reflections and $\varphi_3$ to generate rotations.

    \section{Violations \& Noise}
    \label{sec:violations_noise}
    Causal compatibility inequalities for the Triangle structure (such as those derived in \cref{sec:deriving_inequalities}) offer an avenue into studying quantum non-classicality. In this section, we make use of two methods, exposure to noise and numerical optimization, to further understand the nature of quantum non-classicality in connection to compatibility inequalities.

    In order to parameterize all such distributions, we elect to parameterize the states and measurements separately. Although there are numerous techniques that can used when parameterizing quantum states and measurements~\cite{Petz_2015, Hedemann_2013,Fujii_2005,James_2001,Grasmair_2014,Neilsen_Chaung_2011}, a single technique is presented that was found to be most computationally suitable for our purposes.
    \subsection{Numerical Optimization Results}
    \label{sec:results}

    An alternative explanation has to do with the sensitively of the initial condition $\la_{\br{0}} = \br{\la_{\br{0}, 0}, \ldots, \la_{\br{0}, n}}$ in our optimization. In \cref{sec:param_quantum_dist}, it was shown that our parameter space of choice was $2\pi$-periodic in all entries. Somewhat surprisingly, when using a uniform seed for $\la_0$, all optimization methods consistently converged to inequality saturation instead of inequality violation which of course is achievable by the Fritz distribution. Instead, only initial seeds close enough to the \textit{Fritz parameters} $\la_{\br{\fritz}}$ (the parameters that induce the Fritz distribution using the quantum implementation in \cref{sec:fritz_distribution}) where able to achieve violation. To illustrate this graphically, we let the initial seed be a small Gaussian perturbation $\de \la$ away from $\la_{\br{\fritz}}$ in parameter space.
    \[ \la_{\br{0}} = \la_{\br{\fritz}} + \de \la  \]
    The Gaussian perturbation was given zero mean $\mu = 0$ and variance $\si^2 = \br{2 \pi 10^{\chi}}^2$ where $\chi$ measures an order of magnitude standard deviation. For $I_1$, deviations of $\chi \gtrsim 1.3$ inhibited convergence to violation. This is depicted in \cref{fig:initial_conditions}. Therefore, it is unclear whether or not our results share the same possibilistic structure as $\prob[\fritz]$ because of the inequality itself or the ill-conditioned nature of the optimization. Most likely, this phenomena is due to a combination of both effects.

    \begin{figure}
    \begin{subfigure}[t]{.48\linewidth}
    {\centering\includegraphics[width=\linewidth]{../../figures/optimizations/Gaussian_Perturbation_Fritz_Color_Default.pdf}}
    \caption{For each iteration step $k$, the inequality target decreases.}\label{fig:initial_conditions_a}
    \end{subfigure}
    \begin{subfigure}[t]{.48\linewidth}
    {\centering\includegraphics[width=\linewidth]{../../figures/optimizations/Gaussian_Perturbation_Fritz_Color_Zoomed.pdf}}
    \caption{\Cref{fig:noise} zoomed to show convergence is sensitive to initial conditions.}\label{fig:initial_conditions_b}
    \end{subfigure}
    \caption{Numerical optimizations aimed at violating causal compatibility inequalities are sensitive to initial conditions.}\label{fig:initial_conditions}
    \end{figure}

    The second inequality in consideration is $I_3$; the \textit{symmetric} Web inflation inequality presented in \cref{sec:symmetic_web_inequality}. This inequality was able to achieve a greater relative violation than $I_1$ as optimizations converged to a distribution (\cref{fig:maximum_violation_I_3}) with relative violation $V_F \simeq 2.61$. Just as before, the maximum violating distribution shares a possibilistic structure with the Fritz distribution. However, this result is far more surprising. Since the inequality is symmetric with respect to the exchange of parties $\varphi \in \Perm{A, B, C}$, one would naively expect that the maximum violating distribution is be symmetric as well. If it were not, one could construct a distribution that violates $I_3$ more by symmetrizing $\prob[\fritz]$ by summing over all possible permutations and normalizing. The symmetrized Fritz distribution is plotted in \cref{fig:symmetrized_fritz}. This distribution is also non-classical with relative violation $V_F = 3$. As it turns out, the symmetrized Fritz distribution is \textit{not} quantum-accessible in the sense that is cannot be written as \cref{eq:quantum_model_triangle}\footnote{At least numerical optimizations suggest this is the case.} Therefore we conclude that the space of quantum accessible correlations on the Triangle structure is non-convex; a reiteration of a result found in~\citet{Inflation}.
    \begin{figure}
    \begin{center}
            \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{../../figures/distributions/plotted_dist_I_3_max_violation_2017.pdf}
            \caption{Probability distribution that maximizes violation of $I_3$ from \cref{sec:symmetic_web_inequality} ($V_F \simeq 2.61$).}
            \label{fig:maximum_violation_I_3}
    \end{center}
    \end{figure}
    \begin{figure}
    \begin{center}
            \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{../../figures/distributions/symmetrized_fritz.pdf}
            \caption{Symmetrized version of the Fritz distribution ($V_F \simeq 3$).}
            \label{fig:symmetrized_fritz}
    \end{center}
    \end{figure}

    \section{Conclusions}
    \label{sec:conclusions}
    In \cref{sec:triangle_structure}, we elucidated that compatibility in the Triangle structure has been an unsolved problem for nearly a decade. Initially,~\citet{Branciard_2012} identified the Triangle structure as a challenging causal structure for studying non-classicality. Afterwards,~\citet{Henson_2014} were able to to classify the Triangle structure as \textit{interesting} which partially explains why it remains an enigma. Recently,~\citet{Fritz_2012} discovered the Fritz distribution as the first example of quantum non-classicality in the Triangle structure. Heretofore, researchers have been able to derive causal incompatibility inequalities~\cite{Inflation,Steudel_2010,Henson_2014} but unable to show that any are non-trivial in the context of quantum non-classicality. In \cref{sec:fritz_distribution} the Fritz distribution was described in detail along with Fritz's Problem~\cite[Problem 2.17]{Fritz_2012}.

    In \cref{sec:found_inequalities}, we presented the first examples of causal compatibility inequalities capable of having quantum violations in the sense that they are violated by quantum accessible distributions. This result was made possible through extensive use of the Inflation Technique (\cref{sec:inflation_technique}) when applied to the Fritz distribution. In the context of Fritz's Problem, our result corresponds to a resolution to the following refinement of Fritz's original Problem.
    \begin{enumerate}[label=\textbf{R.\arabic*}]
        \setcounter{enumi}{0}
        \item \label{r:1} Find proofs for causal incompatibility of quantum distributions on the Triangle structure that are \textit{not} reliant on perfect correlations.
    \end{enumerate}

    Ultimately, this work accomplishes two important tasks. First and foremost, the derivation of inequalities such as \cref{eq:ww_ineq} demonstrates the utility of the Inflation technique specifically for quantum causal inference problems. The Inflation Technique was able to derive causal compatibility inequalities that admit quantum violations in the Triangle structure -- a task that no other existing techniques have succeeded at. In this sense, the results of \cref{sec:found_inequalities} showcase how the Inflation technique is capable of generating new proofs of causal incompatibility specifically of quantum distributions for the Triangle structure. Consequently, this work strongly indicates that the Inflation technique has the potential to solve a assortment of unsolved causal inference problems including those manifest in quantum foundations and quantum information theory. Secondly, \cref{sec:noise} demonstrates that the derived causal compatibility inequalities are robust to varying degrees of noise, directly revealing a critical departure from Fritz's original proof of the incompatibility of the Fritz's distribution (\cref{sec:fritz_distribution}) which relies on perfect (non-noisy) correlations. In conclusion \ref{r:1} has been positively solved through the derivation of inequalities such as \cref{eq:ww_ineq} and those found in \cref{sec:web_inequalities}.

    In consideration of out resolution to \ref{r:1}, we additionally propose two more refinements to Fritz's Problem that are concerned more with the nature of the entanglement resource being exploited in a incompatible quantum distribution:
    \begin{enumerate}[label=\textbf{R.\arabic*}]
        \setcounter{enumi}{1}
        \item \label{r:2} Find incompatible quantum distributions on the Triangle structure that require entanglement in more than one shared state.
        \item \label{r:3} Find incompatible quantum distributions on the Triangle structure that satisfy all Bell structure inequalities under Fritz-type embeddings.
    \end{enumerate}

    Fritz's Problem is concerned with identifying incompatible quantum distributions in the Triangle structure that are qualitatively different than the non-classical distributions of the Bell structure discussed in \cref{sec:bell_structure}. When specifically concerned with entanglement resources, Bell structure non-classicality exploits the entanglement of a single bipartite quantum state. In the Triangle structure, the observable nodes $A,B,C$ have access to potentially three different bipartite quantum states. As noted in \cref{sec:fritz_distribution}, the Fritz distribution can be implemented using only a single entangled state\footnote{Of course there exists implementations that make use of three entangled states but at minimum only one is necessary.}. The question, as proposed by \ref{r:2}, remains: does there exist incompatible quantum distributions that genuinely require the entanglement resources of three states? Finding such distributions would affirmatively demonstrate a new form of entanglement resource distinct to the Triangle structure. Moreover \ref{r:3} is justified as a valid interpretation of Fritz's Problem in the following sense: the Fritz distribution was constructed by embedding a quantum distribution incompatible with the Bell structure (\cref{fig:bell_scenario}) into the Triangle structure via the re-imagined version of the Triangle scenario (\cref{fig:triangle_structure_with_fritz_bell_embedded}). Furthermore, the logic of \cref{sec:fritz_distribution} shows that \textit{any} Bell structure compatibility inequality can be upgraded to a compatibility inequality for the Triangle structure, provided one restricts the domain of those inequalities to distributions possessing appropriate perfect correlations. Suppose one relaxed that restriction, then it becomes qualitatively reasonable to associate incompatibility via violations of upgraded inequalities with the same variety of incompatibility that is familiar in the Bell structure. Therefore, satisfying all such upgraded inequalities is a sufficient condition for a new type of incompatibility that is genuinely distinct from Bell structure incompatibility. In summary, it remains unclear whether or not \ref{r:1} or \ref{r:2} is a harder problem or if either is even feasible.

    \section{Summary of Inflation Technique}
    \label{sec:inflation_technique}

    \subsection{Satisfaction of d-Separation Relations}
    \todo[TC]{Absorb the relevant components of the next section into this one}

    \subsection{Marginal Satisfiability and Inequalities}
    \label{sec:deriving_inequalities}

@@

    \subsubsection{The Marginal Problem as a Linear Program}
    \label{sec:marginal_linear}\label{sec:linear_programs}

@@

    % \subsubsection{Events \& Outcomes}
    To every discrete random variable $v$ there corresponds a prescribed set of \term{outcomes} $O_v$. We also define the set of all \term{events over $v$} $\Events{v}$\footnote{In the language of sheaf-theory, $\Events{v}$ is the \textit{sheaf of events}~\cite{Abramsky_2011}.} to be the set of all functions $s : \bc{v} \to O_v$ each representing the event that a measurement on $v$ was made where $s\br{v} \in O_v$ was observed.
    \[ \Events{v} \defined \bc{s : \bc{v} \to O_v} \]
    Evidently, $\Events{v}$ and $O_v$ have a one-to-one correspondence and this distinction can be confounding. There is rarely any harm in referring synonymously to either as outcomes. Nonetheless, a sheaf-theoretic treatment of contextuality~\cite{Abramsky_2011} demands the distinction.
    Specifically for this work, the distinction becomes essential for our discussion and exploit of marginal symmetries in \cref{sec:symmetric_inequalities}. As a natural generalization we define the event over a collection of random variables $V = \bc{v_1, \ldots, v_n}$ in a parallel manner,
    \[ \Events{V} \defined \bc{s: V \to O_{V} \mid \forall i : s\br{v_i} \in O_{v_i} } \eq \label{eq:outcome_space}\]
    Each event $s$ can be compactly represented as a set of mappings over each element of $V$.
    \[ s = \bc{v_1 \mapsto s\br{v_1}, \ldots, v_k \mapsto s\br{v_k}} = \bc{v_i\mapsto s\br{v_i}}_{i = 1}^{k} \]
    The domain $\Dom{s}$ of an event $s$ is the set of random variables it valuates, i.e. if $s \in \Events{V}$, then $\Dom{s} = V$. Under this framework, a probability distribution $\prob[V]$ can be considered as a map from $\Events{V}$ to the unit interval $\bs{0,1}$.
    \begin{example}
        Let $s \in \Events{V}$ be an event over $V$, a probability distribution $\prob[V]$ over $V$ will assign a non-negative probability $\prob[V][s]$ to $s$. Let $V = \bc{v_1, v_2}$ with each $v \in V$ having $3$ distinct outcomes $O_v = \bc{0,1,2}$. Furthermore let $f \in \Events{V}$ be the event $\br{v_1 \mapsto 2, v_2 \mapsto 1}$. The following notations are interchangeable,
        \[ \prob[][s] = \prob[\Dom{s}][s] = \prob[V][s] = \prob[v_1, v_2][s] = \prob[][v_1 \mapsto s_1\br{v_1}, v_2 \mapsto s_2\br{v_2}] = \prob[][v_1 = 2, v_2 = 1] = \prob[v_1v_2][21] \]
        Each of which should be read as ``the probability that $v_1$ got outcome $2$ and $v_2$ got outcome $1$''
    \end{example}
    The marginal problem inherently depends on the concept of probabilistic marginalization. This concept can be understood at the level of events; one event $s \in \Events{V}$ can be ``marginalized'' or restricted to a smaller event $s' \in \Events{W}$ whenever $W \subseteq V$.
    \begin{definition}
    \label{def:section_restriction}
    For every $W \subseteq V$ and $s \in \Events{V}$, the \term{restriction of $s$ onto $W$} (denoted $s|_{W} \in \Events{W}$) is the event in $\Events{W}$ that \textit{agrees} with each of $s$'s assignments for variables in $W$.
    \[ \forall v \in W : s|_{W}\br{v} = s\br{v} \]
    \end{definition}
    % \begin{definition}
    % \label{def:section_compatible}
    % The events $s_{V} \in \Events{V}$ and $s_{W} \in \Events{W}$ are said to be \term{compatible} events if they agree on their valuations of $V \cap W$. Compatibility will be denoted with the infix `$\com$'.
    % \[ s_{V} \com s_{W} \iff {s_{V}}|_{V\cap W} = {s_{W}}|_{V\cap W} \]
    % \end{definition}
    % \begin{definition}
    % \label{def:section_extendable}
    % It $s_V \in \Events{V}$ and $s_W \in \Events{W}$ compatible events and $W \subseteq V$ then $s_W$ is said to be \term{extendable} to $s_V$. Extendability will be denoted with the infix `$\ext$'.
    % \[ s_W \ext s_V \iff s_W \com s_V, W \subseteq V \]
    % Extendability is dual to the notion of a \term{restriction} of $s_V$; $s_V$ can be restricted to $s_W$ ($s_V \res s_W$) if and only if $s_W$ is extendable to $s_V$.
    % \end{definition}

@@

    \subsection{Causal Inflations}
    The \term{Inflation Technique}, invented by \citet{Inflation} and inspired by the \textit{do calculus} and \textit{twin networks} of \citet{Pearl_2009}, is a family of causal inference techniques that can be used to determine if a marginal model $\prob^{\mscenario}$ is compatible or incompatible with a given causal structure $\graph$. As a preliminary summary, the inflation technique begins by \textit{augmenting} a causal structure with additional copies of its nodes, producing an \textit{inflated} causal structure, and then exposes how causal inference tasks on the inflated causal structure can be used to make inferences on the original causal structure. As a example, inflations of the Triangle structure are depicted in \cref{fig:inflations}. Copies of nodes in the inflated causal structure are distinguished by an additional subscript called the \term{copy-index}. For example node $A$ of \cref{fig:triangle_structure} has copies $A_1, A_2, A_3, A_4$ in the \textit{Web inflation} of \cref{fig:the_web_inflation}. All such copies are deemed equivalent via a \term{copy-index equivalence} relation denoted `$\sim$'. A copy-index is effectively arbitrary, so we will refer to an arbitrary inflated copy of $A$ as $A'$.
    \[ A \sim A_1 \sim A' \not\sim B \sim B_1 \sim B' \]
    We preemptively generalize the notion of copy-index equivalence to other mathematical objects like sets, graphs, and groups by saying that $X \sim Y$ if and only if $X = Y$ upon removal of the copy-index. Equipped with the common graph-theoretic terminology and notation of \cref{def:graph_terms}, an inflation can be formally defined as follows:
    \begin{definition}
        An \term{inflation} of a causal structure $\graph$ is another causal structure $\graph'$ such that:
        \[ \forall n' \in \nodes': \AnSub[\graph']{n'} \sim \AnSub[\graph]{n} \eq \label{eq:inflation_defn}\]
        Verbally, for each inflated node $n'$, the ancestral sub-graph of $n'$ in $\graph'$ is equivalent to its counterpart in $\graph$ up to copy-index.
    \end{definition}
    The motivation behind this definition is that if the ancestry of each node $n'$ in $\graph'$ plays the \textit{exact same} role as the ancestry of its source copy $n$ in $\graph$, then every compatible joint distribution $\prob[\nodes]$ on $\graph$ can be used to \textit{create} compatible joint distributions on $\graph'$.
